

---
title: "Homework1"
output: github_document
date: "2022-09-22"
---

# P8105

## Homework 1  **UNI**: _rp3022_

```{r}
library(tidyverse)
```

```{r loading_dataset_penguins}
data("penguins", package = "palmerpenguins")

```

## Problem 1

```{r problem_1 }
a=data.frame(penguins)
nrow(a)
ncol(a)
mean(a$flipper_length_mm, na.rm=TRUE)


```

### Description of the 'dataset penguins'
### The dataset penguins has 344 observations i.e _344 rows_ and 8 variables i.e _8 columns_.The data provides information regarding 344 penguins, and has variables :

* "_species_" which has 3 categories: Adelie, Chinstrap and Gentoo   
* "_island_" which has 3 categories Togerson, Biscoe and Dream.
* "_bill length_", "_bill_depth_mm_",  "_flipper_length_mm_" and "_body_mass_g_": They are continuous numerical variables providing information about the length and depth of their bills and the length of their flippers in mm and their body mass in grams
* "_sex_" dichotomous variable : Male, Female
* "_year_"

### The mean of flipper length is _200.9152_ mm

<<<<<<< HEAD
```{r creating_plots}
ggplot(a, aes(x=bill_length_mm, y=flipper_length_mm, color=species))+geom_point()
ggsave(ggsave ("scatter_a.pdf", height=4, width=6))

```
## Problem 2

```{r Problem_2}
Hw1Q2_df =
    tibble(
    OR = rnorm(n=10),
    Positive_Association = OR > 0,
    Place = c("NewYork", "Asia", "India", "Europe", "Italy", "Paris", "Canada", "Germany", "London", "Boston"),
    Type = factor(c("city", "continent", "country", "continent", "country", "city", "country", "country","city", "city"))
   )
```
### calculating mean for each variable

```{r}
mean_OR = mean(pull(Hw1Q2_df, OR))
round(mean_OR, digits=2)

mean_Positive_Association = mean(pull(Hw1Q2_df, Positive_Association))
round(mean_Positive_Association, digits=2)

mean_Place = mean(pull(Hw1Q2_df, Place))

mean_Type = mean(pull(Hw1Q2_df, Type))
```

### Could not calculate mean for the character and factor variable.


```{r, eval=FALSE}
as.numeric(Hw1Q2_df$vec_char)
as.numeric(Hw1Q2_df$vec_factor)
as.numeric(Hw1Q2_df$vec_logical)

```
## as.numeric was able to convert the factor variable and logical variable to numeric variable.
* For the factor variable, it assigned values 1, 2 and 3 for the 3 levels "city", "continent" and " country" respectively.
* For the logical variable it assigned 1 to the True (OR > 0) and 0 to the false vales (OR<0). The mean of the logical variable was calculated by taking the mean of the "1" and "0" assigned to the true and false logics.

* as.numeric was unable to convert  character variable to numeric variable.

                    


