

---
title: "Homework1"
output: github_document
date: "2022-09-22"
---

# P8105

## Homework 1  **UNI**: _rp3022_

```{r}
library(tidyverse)
```

```{r loading_dataset_penguins}
data("penguins", package = "palmerpenguins")

```

## Problem 1

```{r problem_1 }
a=data.frame(penguins)
nrow(a)
ncol(a)
mean(a$flipper_length_mm, na.rm=TRUE)


```

### Description of the 'dataset penguins'
### The dataset penguins has 344 observations i.e _344 rows_ and 8 variables i.e _8 columns_.The data provides information regarding 344 penguins, and has variables :

* "_species_" which has 3 categories: Adelie, Chinstrap and Gentoo   
* "_island_" which has 3 categories Togerson, Biscoe and Dream.
* "_bill length_", "_bill_depth_mm_",  "_flipper_length_mm_" and "_body_mass_g_": They are continuous numerical variables providing information about the length and depth of their bills and the length of their flippers in mm and their body mass in grams
* "_sex_" dichotomous variable : Male, Female
* "_year_"

### The mean of flipper length is _200.9152_ mm

